An individual differences perspective on the development of pragmatic abilities in the preschool years

### 2022-04-07 paper/manuscript.Rmd
prep submission

abstract: |
  Pragmatic abilities are fundamental to successful language use and learning. Individual differences studies contribute to understanding the psychological processes involved in pragmatic reasoning as well as the link to other cognitive abilities. Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress, however. Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (*N* = 228, 121 female). Studies 1 and 2 assessed the psychometric properties of six pragmatics tasks. Study 3 investigated relations among pragmatics tasks and between pragmatics and other cognitive abilities. The shared cognitive processes were formalized in a computational cognitive model of pragmatic reasoning. The tasks were found to measure stable variation between individuals on a shared latent construct relating to pragmatic inference.

>>>>

abstract: |
  Pragmatic abilities are fundamental to successful language use and learning. Individual differences studies contribute to understanding the psychological processes involved in pragmatic reasoning. Small sample sizes, insufficient measurement tools, and a lack of theoretical precision have hindered progress, however. Three studies addressed these challenges in a sample of three- to five-year-old German-speaking children (N = 228, 121 female). Studies 1 and 2 assessed the psychometric properties of six pragmatics tasks. Study 3 investigated relations among pragmatics tasks and between pragmatics and other cognitive abilities. The shared cognitive processes were formalized in a computational cognitive model of pragmatic reasoning. The tasks were found to measure stable variation between individuals on a shared latent construct relating to pragmatic inference.
